Tree level scattering amplitude in (De)constructed gauge theory

### 2025-04-18 Intermediate report/main.tex
New

\begin{document}
\frame{\titlepage}
\section{Why we need new method?}
\begin{frame}
    \frametitle{Why we need new method?}
    Feynman diagram is a brilliant method without doubt, but it also faces many challenges.
    \begin{itemize}
        \item How to compute high multiplicity amplitudes, like n gluons scattering.
        \item Gauge redundancies bring us many structral complications and non-physical degrees of freedom.
        \item Some symmetries are not manifest in the lagrangian level, like the dual superconformal symmetry for $\mathcal{N}=4$ SYM, etc.
        \item The unexpected simplicity of some amplitudes has led to the speculation that local QFT may not 
        be the most fundamental framework.
    \end{itemize}
\end{frame}
\begin{frame}
    \frametitle{From Frynman diagram to On-shell method}
    On-shell here means that all quantities we use are gauge invariant and satisfy the on-shell condition.
    Specifically, there are many ingredients under this frame
    \begin{itemize}
        \item The analytic continuation for S-matrix.
        \item The color-ordered amplitudes.
        \item The BCFW recursion relation.
        \item The spinor helicity discription for amplitudes.
    \end{itemize}
\end{frame}
\section{Preliminary}
\begin{frame}
    \frametitle{A brief introduction to BCFW}
    BCFW recursion relation is a method to compute scattering amplitude recursively, means that you can 
    compute higher point amplitudes from lower point.
    \par
 \begin{itemize}[label=\textbullet]
    \item Ruth Britto
    \item Freddy Cachazo
    \item Bo Feng
    \item Edward Witten
 \end{itemize}

@@

    Here we consider the case in which all particles are massless, $p_i^2 = 0$ for all $i = 1, 2, \dotsc, n$. We choose two momentum to be shifted oppositely 
    \begin{equation*}
        p_i\rightarrow\hat{p}_i(z)\equiv p_i-zk,\qquad p_j\rightarrow\hat{p}_j(z)\equiv p_j+zk
    \end{equation*}
    satisfying 
    \begin{equation*}
        k^2=0,\qquad p_i\cdot k=0,\qquad p_j\cdot k=0
    \end{equation*}
    Note that,
    \begin{itemize}
        \item Momentum conservation holds for shifted momentum: $\sum_{i=1}^{n}\hat{p}_i^\mu=0$,
        \item Each shifted momentum is still on-shell: $\hat{p}_i^2=0$
        \item For a non-trival subset of generic momenta $\{p_i\}_{i\in I}$, define $P_I^\mu=\sum_{i\in I}p_i^\mu$, $\hat{P}_I^2$ is \textcolor{red}{linear} in z:
              \begin{equation*}
                \hat{P}_I^2=\left(\sum_{i\in I} \hat{p}_i \right) ^2 = P_I^2 -2zP_I\cdot k=-\frac{P_I^2}{z_I}(z-z_I) \quad \text{with} \quad z_I=\frac{P_I^2}{2P_I\cdot k}
              \end{equation*}
    \end{itemize}

\begin{frame}
    \frametitle{Fantasitic result from Cauchy Theorem}
    As a result, we can consider amplitude $A_n$ in terms of shifted momentum $\hat{p}_i^\mu$ instead of original real momentum. 
    \begin{equation*}
        A_n \longrightarrow \hat{A}_n(z)
    \end{equation*}
    and we have known the possible positions of single poles, $z_I$, different propagators give 
    us different single poles in the z-plane. 
    \par
    If we consider the meromorphic function $\frac{\hat{A}_n(z)}{z}$ in the complex plane, pick a contour that surrounds the simple pole at the origin. 
    \textcolor{red}{$\bigstar$ The most important point here is that}
    \begin{equation*}
        \boxed{\color{red}\mathrm{Res}|_{z=0}\frac{\hat{A}_n(z)}{z}=\hat{A}_n(0)=A_n}
    \end{equation*}
    It means that the original amplitude equals to the residue at origin.
\end{frame}
\begin{frame}
    From Cauchy Theorem, we can ontain
    \begin{equation*}
        A_n=-\sum_{z_I}\textrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}+B_n,
    \end{equation*}
    where $B_n$ is the residue of the pole at $z=\infty$, called boundary term.

    Then, at a $z_I$ pole, the propagator $\hat{P}_I^2$ goes to on-shell. In that limit, the shifted amplitude
    \textcolor{red}{factorizes} into to on-shell parts (Unitarity)
    \begin{equation*}
        \hat{A}_n(z)\quad \xrightarrow{z\,\text{near}\,z_I} \quad \hat{A}_L(z_I)\frac{1}{\hat{P}_I^2}\hat{A}_R(z_I)= - \frac{z_I}{z-z_I}\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
    \end{equation*}
    This makes it easy to evaluate the residue at $z=z_I$
    \begin{equation*}
        -Res|_{z=z_I}\frac{\hat{A}_n(z)}{z}=\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)=\raisebox{-1em}{\includegraphics[height=3em]{recrel1.pdf}}   
    \end{equation*}
\end{frame}

\begin{frame}
    \frametitle{Large z behavior}
    In the BCFW formula, the boundary term $B_n$ affects a lot
    \begin{equation*}
        A_n=-\sum_{z_I}Res|_{z=z_I}\frac{\hat{A}_n(z)}{z}+B_n,
    \end{equation*}
    In most applications. one assumes or much better, proves $B_n=0$. This is often justified by declaring a stronger condition
    \begin{equation*}
        \textcolor{red}{\hat{A}_n(z)\rightarrow 0 \quad \text{for} \quad z\rightarrow \infty} 
    \end{equation*}
    Here I show the large z behavior for gluon scattering 
    \begin{center}
        \begin{tabular}{lrc}
            \toprule
            $[i\, \textbackslash \, j\rangle $ & $+$ & $-$ \\
            \midrule
            $+$ & $1/z$ & $z^3$ \\
            $-$ & $1/z$ & $1/z$ \\
            \bottomrule
          \end{tabular}
    \end{center}

@@

\end{frame}
\begin{frame}
\frametitle{Spinor-helicity formalism}
    \begin{itemize}
        \item $\textbf{\text{Massless Case}}$\\
    \begin{equation*}
        p_\mu \sigma^\mu=p_{\alpha\dot{\alpha}}=\lambda_\alpha \tilde{\lambda}_{\dot{\alpha}}=\aket{\lambda}[\lambda|
    \end{equation*}
    There is an ambiguity for the definition, the momentum is invariant under the following redefinition
    \begin{equation*}
        \lambda \rightarrow t^{-1}\lambda, \qquad \tilde{\lambda}\rightarrow t\tilde{\lambda}, \qquad t\in\mathbb{C} 
    \end{equation*}
    same as 
    \begin{equation*}
        \aket{\lambda}\rightarrow t^{-1}\aket{\lambda}, \qquad \sket{\lambda}\rightarrow t\sket{\lambda}
    \end{equation*}
    The scattering amplitudes should transform covariantly under little group scaling:
    \begin{equation*}
        \color{red} \mathcal{A}_n(\{\aket{1},\sket{1},h_1\},\ldots\{t_i^{-1}\aket{i},t_i\sket{i},h_i\},\ldots )=t_i^{2h_i}\mathcal{A}_n
    \end{equation*}
    \end{itemize}
\vspace{-2em}
    \begin{itemize}
    \item \textbf{Massive Case}\\
    It can also be handled in terms of spinor-helicity variable, see also 	arXiv:1709.04891 [hep-th] (Nima Arkani-Hamed, Tzu-Chen Huang, Yu-tin Huang).
    \end{itemize}
\end{frame}

@@

    Because of the constrain from momentum conservation and on-shell condition
    \begin{equation*}
        p_1=\kappa p_3, \qquad p_2=(1-\kappa)p_3 \quad(\text{Collinear})
    \end{equation*}
    All of the contribution 
    \begin{equation*}
        (p_1\cdot p_2),\quad (p_1\cdot p_3),\quad(p_2\cdot p_3)\quad =0  
    \end{equation*}
    In terms of Spinor- Helicity variable, we have 
    \begin{equation*}
        2p_1\cdot p_2=\avg{12}[21]=0\, \longrightarrow \,\avg{12}=[21]^*=0
    \end{equation*}
    \textcolor{red}{You can not obtain any notrvial thing from 3-point!}

    Of coure, you can introduce non-minimal interaction
    \begin{equation*}
        \mathcal{L}_3 \ni \frac{1}{\Lambda^2}\bar{\Psi}\slashed{D}(\Box \Psi)
    \end{equation*}
    but it still equals to 0 in the on-shell case.
\end{frame}

@@

    \textbf{\textcolor{red}{$\star$\,All massless 3-point ampltides are completely determined by little froup scalling!}}

    \textbf{Example}: 3-gluon amplitude\\
    \begin{equation*}
        A_3(g_1^-,g_2^-,g_3^+)=g\frac{\avg{12}^3}{\avg{23}\!\avg{31}}
    \end{equation*}
    There's another possibility 
    \begin{equation*}
        A_3(g_1^-,g_2^-,g_3^+)=g'\frac{[13][23]}{[12]^3}
    \end{equation*}
    but actually it comes from the \textcolor{red}{non-local} interaction $g'AA\frac{\partial}{\square}A$, so we discard it.
\end{frame}
\section{Introduction of quiver gauge theory}
\begin{frame}
    \frametitle{Introduction of Quiver or Moose gauge theory}
    \begin{itemize}
        \item Quiver: A container for carring arrows
        \item Moose: A kind of deer with large horns 
    \end{itemize}

>>>>

\begin{document}
\frame{\titlepage}
\section{Why we need new method?}
\begin{frame}
    \frametitle{Why we need new method?}
Feynman diagram is a brilliant method without doubt, helping us compute the scattering process pertubatively.
\begin{center}

%Curve Lines [id:da3663218891074064] 
\draw    (211.4,171.25) .. controls (275.46,64.25) and (285.26,224.75) .. (345.4,124.75) ;
%Shape: Ellipse [id:dp631421347808582] 
\draw  [color={rgb, 255:red, 134; green, 131; blue, 131 }  ,draw opacity=1 ][fill={rgb, 255:red, 133; green, 128; blue, 128 }  ,fill opacity=1 ] (241.14,136) .. controls (241.14,130.48) and (246.99,126) .. (254.21,126) .. controls (261.43,126) and (267.29,130.48) .. (267.29,136) .. controls (267.29,141.52) and (261.43,146) .. (254.21,146) .. controls (246.99,146) and (241.14,141.52) .. (241.14,136) -- cycle ;
%Curve Lines [id:da0018479507229188785] 
\draw    (345.4,124.75) .. controls (376.12,77.25) and (421.23,156.25) .. (458.49,170.25) ;
%Shape: Ellipse [id:dp37806345751603687] 
\draw  [color={rgb, 255:red, 128; green, 124; blue, 124 }  ,draw opacity=1 ][fill={rgb, 255:red, 133; green, 129; blue, 129 }  ,fill opacity=1 ] (355.53,113.5) .. controls (355.53,107.98) and (361.39,103.5) .. (368.61,103.5) .. controls (375.83,103.5) and (381.68,107.98) .. (381.68,113.5) .. controls (381.68,119.02) and (375.83,123.5) .. (368.61,123.5) .. controls (361.39,123.5) and (355.53,119.02) .. (355.53,113.5) -- cycle ;
%Straight Lines [id:da7438579232631651] 
\draw    (261.4,183.5) -- (426.42,182.76) ;
\draw [shift={(428.42,182.75)}, rotate = 179.74] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Curve Lines [id:da40606602539843883] 
\draw    (316.97,156) .. controls (355.02,142.32) and (265.25,67.01) .. (386.7,69.7) ;
\draw [shift={(388.54,69.75)}, rotate = 181.61] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;

% Text Node
\draw (215.9,175.75) node [anchor=north] [inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small  Gauge Theory}}\\{\fontfamily{ptm}\selectfont {\small  }}};
% Text Node
\draw (219.25,90) node [anchor=north west][inner sep=0.75pt]  [font=\small] [align=left] {{\small {\fontfamily{ptm}\selectfont Kinematic/Color}}\\{\small {\fontfamily{ptm}\selectfont  \ \ \ complexity}}};
% Text Node
\draw (344.1,86.5) node [anchor=north west][inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small Gauge redundancies}}};
% Text Node
\draw (440.24,175.5) node [anchor=north west][inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small S-Matrix}}};
% Text Node
\draw (332.23,166.5) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize] [align=left] {{\fontfamily{ptm}\selectfont {\small \textcolor[rgb]{1,0,0}{?}}}};
% Text Node
\draw (408.97,63) node [anchor=north west][inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small \textbf{\textcolor[rgb]{0.95,0.05,0.05}{Feynman diagrams}}}}};

\end{tikzpicture}
\end{center}
\vspace{-2.3em}
\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt

%Shape: Spring [id:dp43786797179465176] 
\draw   (216.4,104.97) .. controls (219.03,103.2) and (222.94,102.68) .. (226.33,106.02) .. controls (233.1,112.72) and (224.24,121.49) .. (220.86,118.14) .. controls (217.47,114.8) and (226.33,106.02) .. (233.1,112.72) .. controls (239.87,119.41) and (231.01,128.19) .. (227.63,124.84) .. controls (224.24,121.49) and (233.1,112.72) .. (239.87,119.41) .. controls (246.64,126.11) and (237.78,134.88) .. (234.4,131.53) .. controls (231.01,128.19) and (239.87,119.41) .. (246.64,126.11) .. controls (253.41,132.8) and (244.56,141.58) .. (241.17,138.23) .. controls (237.78,134.88) and (246.64,126.11) .. (253.41,132.8) .. controls (254.2,133.59) and (254.78,134.4) .. (255.18,135.22) ;
%Shape: Ellipse [id:dp10564067273276767] 
\draw  [fill={rgb, 255:red, 196; green, 189; blue, 189 }  ,fill opacity=1 ] (252.25,146.07) .. controls (252.25,135.17) and (261.17,126.33) .. (272.19,126.33) .. controls (283.2,126.33) and (292.12,135.17) .. (292.12,146.07) .. controls (292.12,156.97) and (283.2,165.8) .. (272.19,165.8) .. controls (261.17,165.8) and (252.25,156.97) .. (252.25,146.07) -- cycle ;
%Shape: Spring [id:dp8051072896719512] 
\draw   (202.57,146.94) .. controls (203.45,144.19) and (206.11,141.62) .. (210.87,142.09) .. controls (220.4,143.03) and (219.26,154.27) .. (214.5,153.79) .. controls (209.74,153.32) and (210.87,142.09) .. (220.4,143.03) .. controls (229.92,143.98) and (228.78,155.21) .. (224.02,154.74) .. controls (219.26,154.27) and (220.4,143.03) .. (229.92,143.98) .. controls (239.44,144.92) and (238.31,156.15) .. (233.54,155.68) .. controls (228.78,155.21) and (229.92,143.98) .. (239.44,144.92) .. controls (248.97,145.87) and (247.83,157.1) .. (243.07,156.63) .. controls (238.31,156.15) and (239.44,144.92) .. (248.97,145.87) .. controls (250.08,145.98) and (251.05,146.23) .. (251.89,146.59) ;
%Shape: Spring [id:dp24229359788253813] 
\draw   (291.38,147.82) .. controls (292.02,144.73) and (294.46,141.66) .. (299.24,141.73) .. controls (308.81,141.87) and (308.63,154.27) .. (303.84,154.2) .. controls (299.06,154.13) and (299.24,141.73) .. (308.81,141.87) .. controls (318.38,142.01) and (318.2,154.41) .. (313.41,154.34) .. controls (308.63,154.27) and (308.81,141.87) .. (318.38,142.01) .. controls (327.95,142.15) and (327.77,154.55) .. (322.98,154.48) .. controls (318.2,154.41) and (318.38,142.01) .. (327.95,142.15) .. controls (337.52,142.28) and (337.34,154.69) .. (332.55,154.62) .. controls (327.77,154.55) and (327.95,142.15) .. (337.52,142.28) .. controls (338.64,142.3) and (339.63,142.49) .. (340.49,142.8) ;
%Shape: Spring [id:dp1840306550125722] 
\draw   (290.58,139.13) .. controls (289.05,136.36) and (288.91,132.46) .. (292.6,129.45) .. controls (299.99,123.43) and (307.96,133) .. (304.26,136.01) .. controls (300.57,139.02) and (292.6,129.45) .. (299.99,123.43) .. controls (307.38,117.41) and (315.35,126.98) .. (311.65,129.99) .. controls (307.96,133) and (299.99,123.43) .. (307.38,117.41) .. controls (314.77,111.38) and (322.73,120.96) .. (319.04,123.97) .. controls (315.35,126.98) and (307.38,117.41) .. (314.77,111.38) .. controls (322.16,105.36) and (330.12,114.94) .. (326.43,117.95) .. controls (322.73,120.96) and (314.77,111.38) .. (322.16,105.36) .. controls (323.02,104.66) and (323.9,104.17) .. (324.76,103.85) ;
%Shape: Spring [id:dp21851269782703253] 
\draw   (271.73,127.44) .. controls (268.6,126.81) and (265.5,124.41) .. (265.56,119.67) .. controls (265.68,110.2) and (278.2,110.35) .. (278.14,115.09) .. controls (278.08,119.82) and (265.56,119.67) .. (265.68,110.2) .. controls (265.79,100.73) and (278.32,100.88) .. (278.26,105.61) .. controls (278.2,110.35) and (265.68,110.2) .. (265.79,100.73) .. controls (265.91,91.25) and (278.44,91.4) .. (278.38,96.14) .. controls (278.32,100.88) and (265.79,100.73) .. (265.91,91.25) .. controls (266.03,81.78) and (278.55,81.93) .. (278.5,86.67) .. controls (278.44,91.4) and (265.91,91.25) .. (266.03,81.78) .. controls (266.04,80.67) and (266.23,79.69) .. (266.54,78.84) ;
%Shape: Spring [id:dp05024762380258474] 
\draw   (224.2,195.95) .. controls (222.44,193.32) and (221.96,189.44) .. (225.37,186.13) .. controls (232.21,179.5) and (240.98,188.36) .. (237.56,191.68) .. controls (234.14,194.99) and (225.37,186.13) .. (232.21,179.5) .. controls (239.05,172.87) and (247.82,181.73) .. (244.4,185.05) .. controls (240.98,188.36) and (232.21,179.5) .. (239.05,172.87) .. controls (245.88,166.24) and (254.65,175.1) .. (251.24,178.42) .. controls (247.82,181.73) and (239.05,172.87) .. (245.88,166.24) .. controls (252.72,159.61) and (261.49,168.47) .. (258.07,171.79) .. controls (254.65,175.1) and (245.88,166.24) .. (252.72,159.61) .. controls (253.52,158.83) and (254.35,158.27) .. (255.18,157.88) ;
%Shape: Spring [id:dp9217960437924791] 
\draw   (283.39,161.81) .. controls (286.03,160.03) and (289.94,159.51) .. (293.32,162.86) .. controls (300.09,169.56) and (291.24,178.33) .. (287.85,174.98) .. controls (284.47,171.64) and (293.32,162.86) .. (300.09,169.56) .. controls (306.86,176.25) and (298.01,185.03) .. (294.62,181.68) .. controls (291.24,178.33) and (300.09,169.56) .. (306.86,176.25) .. controls (313.63,182.95) and (304.78,191.72) .. (301.39,188.37) .. controls (298.01,185.03) and (306.86,176.25) .. (313.63,182.95) .. controls (320.4,189.64) and (311.55,198.42) .. (308.17,195.07) .. controls (304.78,191.72) and (313.63,182.95) .. (320.4,189.64) .. controls (321.2,190.43) and (321.78,191.24) .. (322.17,192.06) ;

% Text Node
\draw (254.1,174.78) node [anchor=north west][inner sep=0.75pt]    {$\cdots $};
% Text Node
\draw (354,136) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont Can we really compute this by hand?}};

\end{frame}
\begin{frame}
    \frametitle{From Frynman diagram to On-shell method}
    The answer is On-shell method.
    \begin{center}

%Straight Lines [id:da5445374886882226] 
\draw    (276.25,137) -- (457.5,136.26) ;
\draw [shift={(459.5,136.25)}, rotate = 179.77] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;

% Text Node
\draw (233.4,128.25) node [anchor=north] [inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small  Gauge Theory}}\\{\fontfamily{ptm}\selectfont {\small  }}};
% Text Node
\draw (463.24,129.5) node [anchor=north west][inner sep=0.75pt]  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small S-Matrix}}};
% Text Node
\draw (317.73,117.5) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize] [align=left] {{\fontfamily{ptm}\selectfont {\small \textbf{\textcolor[rgb]{0.95,0.04,0.04}{On-shell method}}}}};

    \end{center}

    On-shell here means that all quantities we use are gauge invariant and satisfy the on-shell condition.
    Specifically, there are many ingredients under this frame
    \begin{itemize}
        \item The analytic continuation for S-matrix.
        \item The color-ordered amplitudes.
        \item The BCFW recursion relation.
        \item The spinor helicity discription for amplitudes.
    \end{itemize}
\end{frame}
\section{Preliminary}
\begin{frame}
    \frametitle{A brief introduction to BCFW}
BCFW helps us solve one of the problems
\vspace{-1em}
\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{BCFW.png}
\end{figure}
\vspace{-1em}
with the cost of introducing \textcolor{red}{complexed momentum}.

BCFW is a method to compute amplitudes recursively, proposed by 
\begin{itemize}
    \item Britto, Cachazo, Feng, arXiv: hep-th/0412308
    \item Britto, Cachazo, Feng, Witten, arXiv: hep-th/0501052

\end{itemize}

@@

    Here we consider the case in which all particles are massless, $p_i^2 = 0$ for all $i = 1, 2, \dotsc, n$. We choose two momentum to be shifted oppositely 
    \begin{equation*}
        p_i\rightarrow\hat{p}_i(z)\equiv p_i-zk,\qquad p_j\rightarrow\hat{p}_j(z)\equiv p_j+zk
    \end{equation*}
    satisfying 
    \begin{equation*}
        k^2=0,\qquad p_i\cdot k=0,\qquad p_j\cdot k=0
    \end{equation*}

\begin{figure}
    \centering
    \begin{minipage}{0.45\textwidth}
        \tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt

\begin{tikzpicture}[scale=0.7,x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300

%Shape: Circle [id:dp47058391497271046] 
\draw  [fill={rgb, 255:red, 151; green, 145; blue, 145 }  ,fill opacity=1 ] (266.75,126) .. controls (266.75,112.19) and (277.94,101) .. (291.75,101) .. controls (305.56,101) and (316.75,112.19) .. (316.75,126) .. controls (316.75,139.81) and (305.56,151) .. (291.75,151) .. controls (277.94,151) and (266.75,139.81) .. (266.75,126) -- cycle ;
%Straight Lines [id:da8759716500759761] 
\draw    (249,78.25) -- (273.5,109.25) ;
%Straight Lines [id:da2121821831988906] 
\draw    (233.5,103.25) -- (266.5,120.75) ;
%Straight Lines [id:da6378763431676462] 
\draw  [dash pattern={on 0.84pt off 2.51pt}]  (350.75,54.38) -- (350.75,126.25) -- (350.75,187.63) ;
%Straight Lines [id:da7508961107891289] 
\draw  [dash pattern={on 0.84pt off 2.51pt}]  (248.25,124) -- (248.5,142.25) ;
%Straight Lines [id:da06317949320750826] 
\draw    (237,155.25) -- (271.5,140.75) ;
%Straight Lines [id:da403008866951158] 
\draw    (261.5,180.25) -- (281.5,149.25) ;
%Straight Lines [id:da8334043101335312] 
\draw    (423,119.25) -- (457.5,104.75) ;
%Straight Lines [id:da03451573841415356] 
\draw    (418.5,109.75) -- (438.5,78.75) ;
%Straight Lines [id:da025418352459996796] 
\draw    (420,140.25) -- (453,157.75) ;
%Straight Lines [id:da22879254297825424] 
\draw  [dash pattern={on 0.84pt off 2.51pt}]  (442.25,121) -- (442.5,139.25) ;
%Straight Lines [id:da2355772127149045] 
\draw    (410.5,148.75) -- (435,179.75) ;
%Shape: Rectangle [id:dp6752662310096104] 
\draw   (328,54.25) -- (328,198.75) -- (212,198.75) -- (212,54.25) -- cycle ;
%Straight Lines [id:da4580921639862495] 
\draw    (316.75,126) -- (373.5,125.75) ;
%Shape: Circle [id:dp8699671429684472] 
\draw  [fill={rgb, 255:red, 151; green, 145; blue, 145 }  ,fill opacity=1 ] (373.5,125.75) .. controls (373.5,111.94) and (384.69,100.75) .. (398.5,100.75) .. controls (412.31,100.75) and (423.5,111.94) .. (423.5,125.75) .. controls (423.5,139.56) and (412.31,150.75) .. (398.5,150.75) .. controls (384.69,150.75) and (373.5,139.56) .. (373.5,125.75) -- cycle ;

% Text Node
\draw (239.75,58.4) node [anchor=north west][inner sep=0.75pt]    {$\hat{i}$};
% Text Node
\draw (447.47,58.4) node [anchor=north] [inner sep=0.75pt]    {$\hat{j}$};
% Text Node
\draw (250.75,177.9) node [anchor=north west][inner sep=0.75pt]    {$n$};
% Text Node
\draw (224.25,147.4) node [anchor=north west][inner sep=0.75pt]    {$1$};
% Text Node
\draw (424.25,176.9) node [anchor=north west][inner sep=0.75pt]    {$n-1$};
% Text Node
\draw (268.75,34.4) node [anchor=north west][inner sep=0.75pt]  [color={rgb, 255:red, 241; green, 12; blue, 12 }  ,opacity=1 ]  {$I$};

\end{tikzpicture}
    \end{minipage}
    \hspace{1em}
    \begin{minipage}{0.45\textwidth}
        For a non-trival subset of generic momenta $\{p_i\}_{i\in I}$
    \begin{equation*}
        \hat{P}_I^2=P_I^2 -2zP_I\cdot k=-\frac{P_I^2}{z_I}(z-z_I) 
    \end{equation*}

    with $\textcolor{red}{\quad z_I=\frac{P_I^2}{2P_I\cdot k}}$.  
    \end{minipage}
\end{figure} 
\end{frame}

\begin{frame}
    \frametitle{Fantasitic result from Cauchy Theorem}
    %First, I will show the most important part in this report.
    \begin{block}{BCFW recursion relation}
        \begin{equation*}
            A_n=\sum_{\text{diagrams}\,I}\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)=\sum_{\text{diagrams}\,I}\raisebox{-1.3em}{\includegraphics[height=3em]{recrel1.pdf}}
        \end{equation*}
    \end{block}
    Brief proof:

    We consider amplitude $A_n$ in terms of shifted momentum $\hat{p}_i^\mu$ instead of original real momentum. 
    \begin{equation*}
        A_n \longrightarrow \hat{A}_n(z)
    \end{equation*}

    If we consider the meromorphic function $\frac{\hat{A}_n(z)}{z}$ in the complex plane, pick a contour that surrounds the simple pole at the origin. 
    \textcolor{red}{$\bigstar$ The most important point here is that}
    \begin{equation*}
        \boxed{\color{red}\mathrm{Res}|_{z=0}\frac{\hat{A}_n(z)}{z}=\hat{A}_n(0)=A_n}
    \end{equation*}
    It means that the original amplitude equals to the residue at origin.
\end{frame}
\begin{frame}
    From Cauchy Theorem, we can ontain
    \begin{equation*}
        A_n=-\sum_{z_I}\textrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}+B_n,
    \end{equation*}
    where $B_n$ is the residue of the pole at $z=\infty$, called boundary term.
    \vspace{-1em}
    \begin{figure}[htbp]
        \centering
        \includegraphics[width=0.3\textwidth]{CT.png}
    \end{figure}
    \vspace{-1.5em}
    %Then, at a $z_I$ pole, the propagator $\hat{P}_I^2$ goes to on-shell. In that limit, the shifted amplitude
    %\textcolor{red}{factorizes} into to on-shell parts (Unitarity)
    \begin{equation*}
        \hat{A}_n(z)\quad \xrightarrow{z\,\text{near}\,z_I} \quad \hat{A}_L(z_I)\frac{1}{\hat{P}_I^2}\hat{A}_R(z_I)= - \frac{z_I}{z-z_I}\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
    \end{equation*}
    This makes it easy to evaluate the residue at $z=z_I$
    \begin{equation*}
        -\mathrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}=\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
    \end{equation*}
\end{frame}

\begin{frame}
    \frametitle{Large z behavior}
    In the BCFW formula, the boundary term $B_n$ affects a lot
    \begin{equation*}
        A_n=-\sum_{z_I}\mathrm{Res}|_{z=z_I}\frac{\hat{A}_n(z)}{z}+B_n,
    \end{equation*}
    In most applications. one assumes or much better, proves $B_n=0$. This is often justified by declaring a stronger condition
    \begin{equation*}
        \textcolor{red}{\hat{A}_n(z)\rightarrow 0 \quad \text{for} \quad z\rightarrow \infty} 
    \end{equation*}
    Here I show the large z behavior for gluon scattering 
    \begin{center}
        \begin{tabular}{lrc}
            \toprule
            $[i\, \textbackslash \, j\rangle $ & $+$ & $-$ \\
            \midrule
            $+$ & $1/z$ & $z^3$ \\
            $-$ & $1/z$ & $1/z$ \\
            \bottomrule
          \end{tabular}
    \end{center}

@@

\end{frame}
\begin{frame}
\frametitle{Spinor-helicity formalism}
    \begin{itemize}
        \item $\textbf{\text{Massless Case}}$\\
    \begin{equation*}
        p_\mu \sigma^\mu=p_{\alpha\dot{\alpha}}=\lambda_\alpha \tilde{\lambda}_{\dot{\alpha}}=\aket{\lambda}[\lambda|
    \end{equation*}
    There is an ambiguity for the definition, the momentum is invariant under the following redefinition
    \begin{equation*}
        \lambda \rightarrow t^{-1}\lambda, \qquad \tilde{\lambda}\rightarrow t\tilde{\lambda}, \qquad t\in\mathbb{C} 
    \end{equation*}
    same for
    \begin{equation*}
        \aket{\lambda}\rightarrow t^{-1}\aket{\lambda}, \qquad \sket{\lambda}\rightarrow t\sket{\lambda}
    \end{equation*}
    The scattering amplitudes should transform covariantly under little group scaling:
    \begin{equation*}
        \color{red} \mathcal{A}_n(\{\aket{1},\sket{1},h_1\},\ldots\{t_i^{-1}\aket{i},t_i\sket{i},h_i\},\ldots )=t_i^{2h_i}\mathcal{A}_n
    \end{equation*}
    \end{itemize}
\vspace{-2em}
    \begin{itemize}
    \item \textbf{Massive Case}\\
    It can also be handled in terms of spinor-helicity variable, see also 	arXiv:1709.04891 [hep-th] (Nima Arkani-Hamed, Tzu-Chen Huang, Yu-tin Huang).
    \end{itemize}
\end{frame}

@@

    Because of the constrain from momentum conservation and on-shell condition
    \begin{equation*}
        p_1=\kappa p_3, \qquad p_2=(1-\kappa)p_3 \quad(\text{Collinear})
    \end{equation*}
    All of the contribution 
    \begin{equation*}
        (p_1\cdot p_2),\quad (p_1\cdot p_3),\quad(p_2\cdot p_3)\quad =0  
    \end{equation*}
    In terms of Spinor- Helicity variable, we have 
    \begin{equation*}
        2p_1\cdot p_2=\avg{12}[21]=0\, \longrightarrow \,\avg{12}=[21]^*=0
    \end{equation*}
    \textcolor{red}{We can not obtain any thing nontrival from 3-point!}

    Of coure, you can introduce non-minimal interaction
    \begin{equation*}
        \mathcal{L}_3 \ni \frac{1}{\Lambda^2}\bar{\Psi}\slashed{D}(\Box \Psi)
    \end{equation*}
    but it still equals to 0 under the on-shell condition.
\end{frame}

@@

    \textbf{\textcolor{red}{$\star$\,All massless on-shell 3-point ampltides are completely determined by little group scaling!}}

    \textbf{Example}: 3-gluon amplitude\\
    \begin{equation*}
        A_3(g_1^-,g_2^-,g_3^+)=g\frac{\avg{12}^3}{\avg{23}\!\avg{31}}
    \end{equation*}
    There's another possibility 
    \begin{equation*}
        A_3(g_1^-,g_2^-,g_3^+)=g'\frac{[13][23]}{[12]^3}
    \end{equation*}
    but actually it comes from the \textcolor{red}{non-local} interaction $g'AA\frac{\partial}{\square}A$, so we discard it.
\end{frame}
\section{Introduction of quiver gauge theory}
\begin{frame}
    \frametitle{Introduction of Quiver or Moose gauge theory}
    \begin{figure}
        \centering
        \begin{minipage}{0.45\textwidth}
        Quiver: A container for carring arrows\\
        Moose: A kind of deer with large horns 
    \end{minipage}
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.3\linewidth]{Quiver.jpg}
        \hspace{1em}
        \includegraphics[width=0.3\textwidth]{Moose.jpeg}

    \end{minipage}
\end{figure}
